%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Souranil Das}} & Email: \href{mailto:souranil.das@gmail.com}{souranil.das@gmail.com}\\
  \href{https://linkedin.com/in/souranild}{LinkedIn: linkedin.com/in/souranild} & Mobile:~~~+91-700-8459-203 \\
  \href{https://github.com/souranild}{Github: ~~github.com/souranild} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Chennai, India}
      {Bachelor of Technology - Electronics and Communication;  GPA: 3.23/4.0}{2019 - 2023}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures \& Algorithms, VLSI, IOT, Computer Networks}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~SystemVerilog, C/C++, Python, Bash}
	\resumeSubItem{Technologies}{~~~~IoT, Embedded Systems, RTL Design, Automation, JTAG, Ethernet}
	\resumeSubItem{Verification}{~~~~Functional Verification, Assertion-Based Verification, UVM, SystemVerilog}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{NXP Semiconductors}{Bengaluru, India}
    {Design Verification Engineer - G2}{Apr 2024 – Present}
    \resumeItemListStart
        \item \textbf{Working} on an ethernet based multi interface automotive hub.
        \item \textbf{Working} on an internal tool for simplifying test running, and monitoring.
        \item Successfully completed \textbf{4} tape-outs.
      \resumeItemListEnd
    \resumeSubheading{NXP Semiconductors}{Bengaluru, India}
    {Design Verification Engineer - G1}{Jul 2023 – Apr 2024}
    \resumeItemListStart
        \item \textbf{Worked} on updates on Matrix LED Controller, which provides smart automotive headlights and backlights.
        \item Completed \textbf{two} incremental tape-outs.
        \item \textbf{Automated} and made DV work environments better by bringing in things learnt from Software Validation.
      \resumeItemListEnd
\vspace{-5pt}
    \resumeSubheading
		{NXP Semiconductors}{Hyderabad, India}
		{Software Validation \& Automation Intern}{Sept 2022 – July 2023}
		\resumeItemListStart
        \item \textbf{Developed} tests and automation scripts for Realtime Edge IoT platform
        \item \textbf{Shipped} \textbf{3} successful releases with fully automated regression setups
		\resumeItemListEnd
    \resumeSubheading
		{Samsung Electronics}{Bengaluru, India}
		{Project Intern}{June 2021 – Jan 2022}
		\resumeItemListStart
        \item \textbf{Developed} an internal web application using ReactJS, Flask, and TensorFlow for image and video annotation.
        \item \textbf{Integrated} Advanced ML Models: Incorporated SSD, RCNN, and YOLOv3 for data testing and batch processing workflows.
		\resumeItemListEnd
    \resumeSubheading
		{Yuan-Ze University}{Taoyuan, Taiwan}
		{IoT Research Intern}{June 2022 – March 2023}
		\resumeItemListStart
        \item \textbf{Collaborated} with YZU Taiwan students to design a Smart Hydroponic System with sensors and automation for basil growth.
        \item \textbf{Developed} a Smart Hydroponic System, involving hardware and software co-creation. Achieved a fully automated system for monitoring indoor organic vegetable growth, including testing various hydroponic solutions, sensor combinations and reporting plant vitals.
		\resumeItemListEnd
    \resumeSubheading
		{IEEE Photonics}{Chennai, India}
		{Vice President}{July 2020 – July 2021}
		\resumeItemListStart
        \item \textbf{Headed} the development of the society's website and collaborating on tasks such as scheduling talks.
        \item \textbf{Managed} administrative functions, contributing to the smooth operation of the Society.
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://docs.google.com/document/d/1O1YsuZPpMzv1nlXXJV094MKD4nJhtZU2g33nz0zF3LI/edit}{AI Annotation Tool for Data Testing} (ReactJS, Flask, TensorFlow, SSD, RCNN, YOLOv3)}{Developed a full-stack web application for image and video annotation. Integrated object detection models. Deployed internally for data testing and batch processing workflows. (Jun 2021 - Jan 2022)}
\vspace{2pt}
\resumeSubItem{\href{https://github.com/souranild/8051sec}{Access Control System using 8051 Microcontroller and DC Motor} (Microcontroller, RFID)}{Developed an RFID-based access control system using 8051 microcontroller. Enabled motor control for authorized entries, unauthorized access alerts, and real-time entry count tracking. (Feb 2021 – Jun 2021)}
\vspace{2pt}
\resumeSubItem{\href{https://docs.google.com/document/d/1T75HzlptJYIZZojti-dx1BhP0im88-l5l7B-8dgqOQI/edit?usp=sharing}{Remote Video Surveillance Wireless Robot} (Wi-Fi, Video Streaming, Object Detection)}{Built a Wi-Fi controlled robot with live video streaming, object/person detection, and intrusion alerts. Controlled via web server and Android app for remote surveillance. (Feb 2021 – Jun 2021)}
\vspace{2pt}
\resumeSubItem{\href{https://docs.google.com/document/d/1x4zfeQhCVb3S7J35QM56Sth9_4soquWMxKuBpIZtCDQ/edit?usp=sharing}{Garduino - Automatic Garden Management with Arduino} (Arduino, IoT, Wi-Fi)}{Designed and built an Arduino-based smart garden system with both manual and automatic plant watering capabilities. Enabled remote monitoring and control via smartphone using Wi-Fi, providing real-time plant status updates and user interaction. (Apr 2020 – Sep 2020)}
\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://ieeexplore.ieee.org/document/10198435}{Revolutionizing Holy-Basil Cultivation with AI-Enabled Hydroponics System} (IEEE Access, 2023)}{Co-authored the paper published in IEEE Access, vol. 11, pp. 82624–82639. The work integrates hydroponics, IoT, and machine learning to optimize holy-basil cultivation with real-time monitoring and healthiness scoring.}
\vspace{2pt}
\resumeSubItem{\href{https://doi.org/10.1007/978-3-031-11633-9_19}{SMADE - Smart Medical Assist Device} (Springer, 2022)}{Co-authored the paper published in Computer, Communication, and Signal Processing (ICCCSP 2022), IFIP AICT vol. 651. Developed a device for elderly care integrating medication scheduling and real-time vitals monitoring.}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------CERTIFICATIONS-----------------
\section{Certifications}
\begin{description}[font=$\bullet$]
\item {\href{https://verificationacademy.com/courses/assertion-based-verification}{Assertion-Based Verification} - Mentor Graphics, Sep 2023}
\vspace{-5pt}
\item {\href{https://www.linkedin.com/in/souranild/details/certifications/1635541591437/single-media-viewer}{Essential SystemVerilog for UVM} - Cadence, Sep 2023}
\vspace{-5pt}
\item {\href{https://www.credential.net/6c3989e0-fd5c-456a-b3a6-d2a782bca74f}{Designing and Modelling of IoT, AI \& ML Systems} - Arm, Aug 2022}
\vspace{-5pt}
\item {\href{https://www.credly.com/badges/dba3eefa-3ac0-44e8-849f-2ccfcf4cf768/public_url}{AWS Certified Cloud Practitioner} - Amazon Web Services, Jun 2022}
\end{description}

\end{document}